---
title: "Team-89 Group Project Modeling V3"
author: "Madhu Mudigonda"
date: '2022-06-25'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initialize the required libraries

```{r echo=FALSE}
library('TTR')
library('quantmod')

library(ggplot2); library(readr); library(dplyr); library(tidyverse);
library(gridExtra);library("ggExtra"); library(knitr);
library(caret); library(gridExtra); library(lubridate); library(stringr);
library(PerformanceAnalytics); library(xts); library(tidyquant); library(tidyverse);library(corrplot)
```
## Load gun company stock data
```{r Load Gun co company stock data, include=TRUE}

date_str <- "2009-10-01"
stocks <- c("rgr", "swbi", "oln", "npk", "bgfv", "axon" )

gun_co_stocks <- stocks %>% tq_get(get="stock.prices", from=date_str, to=Sys.Date())
head(gun_co_stocks)



```



## Get stock daily ajusted returns
```{r Compute adjusted daily returns, include=TRUE}
gun_co_returns <- gun_co_stocks %>% group_by(symbol) %>% tq_transmute(select = adjusted, 
                                                                      mutate_fun = periodReturn, 
                                                                      period="daily", 
                                                                      col_rename = "adjusted_returns")
head(gun_co_returns)

```


## Create a portfolio of gun manufactures with market weighted index weights. Market caps as of 06/25/2022

```{r data scaling, portfolio weights, include=TRUE}

rgr_mrkt_cap  <- 1165000000  
swbi_mrkt_cap <- 748193000  
Olin_mrkt_cap <- 7085000000 
npk_mrkt_cap  <- 462936000
bgfv_mrkt_cap <- 268815000
axon_mrkt_cap <- 6828000000

total <- rgr_mrkt_cap + swbi_mrkt_cap + Olin_mrkt_cap + npk_mrkt_cap + bgfv_mrkt_cap + axon_mrkt_cap

gun_wts <- c(rgr_mrkt_cap/total, swbi_mrkt_cap/total, Olin_mrkt_cap/total,
             npk_mrkt_cap/total, bgfv_mrkt_cap/total, axon_mrkt_cap/total)
gun_co_portfolio_returns <- gun_co_returns %>% 
                                tq_portfolio(assets_col = symbol, 
                                             returns_col = adjusted_returns, 
                                             weights = gun_wts, 
                                             col_rename = "adjusted_returns")

gun_co_portfolio_returns <- gun_co_portfolio_returns %>% mutate(gunDD = Drawdowns(adjusted_returns))

head(gun_co_portfolio_returns, 10)
```

## Compute short term and long term Simple moving average 

```{r Create SMA factors, include=TRUE}
gun_co_portfolio_returns <- gun_co_portfolio_returns %>%
  # Calculate 50-day simple moving average
                           tq_mutate(select = adjusted_returns, mutate_fun = SMA, n = 2) %>%
                           # Rename 50-day SMA to SMA.short
                           rename(SMA.short = SMA) %>%
                           tq_mutate(select = adjusted_returns, mutate_fun = SMA, n = 3) %>%
                           rename(SMA.long = SMA)
                                    
gun_co_portfolio_returns <- gun_co_portfolio_returns %>% filter(date>="2010-01-01")

                                     
head(gun_co_portfolio_returns, 10)
```



## Mass shootings data, Filter mass shootings that happened after 2010-01-01 and fatalities>=5, then Obtain mass shooting date vector, shift the weekend dates to following week dates
```{r Load US mass shootings data and clean data, include=TRUE}
us_mass <- read.csv("US_Mass_Shootings_May_24_2022.csv")

#Select those variables that are needed for our analysis
us_mass02 <- us_mass %>% select(location, date, fatalities, injured, total_victims)

# change date format to standardize dates
us_mass02 <- us_mass02 %>% mutate(date = mdy(date)) %>%
                mutate(year = year(date)) %>%
                mutate(state = ifelse(location=="Washington, D.C.", "Washington, D.C.",str_extract(location,
                                                "[\\s]*[A-Z][a-z]+[\\s]*[[A-Z][a-z]+]*$"))) %>%
                mutate(fatalities = as.integer(fatalities)) %>%
                mutate(injured = as.integer(injured)) %>%
                mutate(total_victims = as.integer(total_victims)) %>%
                select(location, state, date, year, fatalities, injured, total_victims)

us_mass03 <- us_mass02 %>% filter(date>="2010-01-01" & fatalities>=5)

us_mass03$orig_date = us_mass03$date
us_mass03 %>%
     mutate(new_date = case_when(weekdays(date) == "Saturday" ~ (date + 2), 
                                 weekdays(date) == "Sunday" ~ (date + 1), 
                                 TRUE ~ date)) %>%
     select(-date)

head(us_mass02, 10)

```


## Merge Gun Portfolio returns vs US mass shootings data and correlation plots:

```{r merge gun co stock data with US mass shooting data, include=TRUE}

us_mass03$event_date <- us_mass03[,8]

gun_co_portfolio_returns$return_date <- gun_co_portfolio_returns$date

merged_df <- merge(x=gun_co_portfolio_returns, y=us_mass03, by.x="date", by.y="event_date",  all.x = TRUE)


merged_df$featured <- ifelse(!is.na(merged_df$total_victims), 1, 0)

# fill nas where there are no events with 0
merged_df$total_victims <- ifelse(is.na(merged_df$total_victims), 0, merged_df$total_victims)
merged_df$fatalities <- ifelse(is.na(merged_df$fatalities), 0, merged_df$fatalities)
merged_df$injured <- ifelse(is.na(merged_df$injured), 0, merged_df$injured)

merged_df_select_columns <- merged_df[, c("adjusted_returns", "SMA.short", "SMA.long", 
                                          "fatalities", "injured", "total_victims", "featured" )]

corrplot(cor(merged_df_select_columns))

cor_data = cor(merged_df_select_columns)

cor_data

```

## Create model:

```{r create model, include=TRUE}

linear_model <- lm(SMA.short ~ injured + fatalities + total_victims, data=merged_df)
summary(linear_model)

```
